{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-08 documents/pseudo_soliton.tex
tests
More propagation
Stuff

Precursor waves do not appear to be explicitly mentioned in current standards, but are implicitly governed by the Fourier-spectrum clauses. Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz. We can make some mechanistic claims.

@@

>>>>

Precursor waves do not appear to be explicitly mentioned in C95- but are implicitly governed by the Fourier-spectrum clauses. Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz. We can make some mechanistic claims.

@@

As saliently noted by Adair:

\begin{quote}
	“the energy of the pulse at a depth of 1 cm is about 0.8% of the initial energy;
	the maximum electric field strength, E is reduced by a factor of about 12, and the maximum rate-ofchange of the field, dE/dt, is reduced by a factor of 20. Every characteristic of the pulse at depth is
	contained, albeit attenuated, in the initial pulse. Consequently, we do not find it credible that the
	strongly attenuated pulse – albeit with a different shape – can induce biological effects beyond that of
	the initial pulse.”
\end{quote}

The 2018 NATO Research Task Group 189 report \cite{treatyelectromagnetic} is an excellent source of data for these.

\begin{quote}
	Other basic bioeffects research [50], [52], [53], [66], [81], [83] has failed to provide support for Albanese’s multiple	theoretical postulates.
\end{quote}

The real killer

temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited

### 2020-10-08 documents/supplemental.tex
Stuff

@@

@@

Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; manganese dioxide catalyzed decomposition of hydrogen peroxide. MnO2 is readily obtained from alkaline batteries; and in this case no sterility issues are presented. However, it is not obvious how all h2o2 vapor can be prevented from contacting the culture.

@@

In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to the cabinet.

Shaking incubators, which simply rock the

In our case, ensuring that a great deal of headspace was present in the tube was sufficient for brief growth.

>>>>

Phage releases several amino acids such as putrescine and spermadine when broken. These can be indicated at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.

@@

A lot of the basic facts of phage were determined in the 1930s;

@@

Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; the Manganese dioxide catalyzed decomposition of hydrogen peroxide. $MnO_2$ is readily obtained from alkaline batteries; and in this case no sterility issues are presented. However, it is not obvious how antimicrobial $H_2O_2$ vapor can be prevented from contacting the culture.

@@

In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to an enclosing cabinet.

Shaking incubators, where the flasks are

Ensuring that a great deal of headspace was present in a sealed tube (that is, culturing 2.5 mL in a 15 mL falcon tube) was sufficient for brief, low-density.
